Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Insect Populations and Diseases?

### 2017-08-25 analysis/paper/paper.tex
Add eps file and edit title of paper

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates
Affect Rice Pests and Diseases?} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
\\
A.H. Sparks\textsuperscript{\getAff{University of Southern Queensland}}\textsuperscript{*},
N.P. Castilla\textsuperscript{\getAff{International Rice Research Institute}},
B.A.R. Hadi\textsuperscript{\getAff{International Rice Research Institute}},
B.O. Sander\textsuperscript{\getAff{International Rice Research Institute}}\\
\bigskip
\textbf{\getAff{University of Southern Queensland}}Centre for Crop Health, West Street, Toowoomba, Queensland, Australia,
4350\\
\textbf{\getAff{International Rice Research Institute}}Los Baños, Laguna, Philippines, 4031\\
\bigskip
* Corresponding author: adam.sparks@usq.edu.au\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Water and nitrogen management play vital roles in rice production.
However, the mismanagement of these two management practices may trigger
sheath blight of rice, caused by \emph{Rhizoctonia solani}, which is
favored by wet conditions, high relative humidity, and high nitrogen
fertilizer levels. To understand how different combinations of water and
nitrogen management affect sheath blight epidemics, we conducted two
separate split-plot experiments with a water saving (alternate wetting
and drying) regime and traditional flood irrigation regime combined with
differing nitrogen treatments in the dry seasons of 2015 and 2016.
Disease was scored in the same way in both experiments using a sheath
blight assessment scale for field evaluation developed at the
International Rice Research Institute to assess the severity on infected
sheaths and leaves while sheath blight incidence on tillers were counted
per hill. We were unable to detect any differences in disease in either
experiment due to irrigation regime, N rates or the interaction of the
two treatments in either season. This suggests that farmers can adopt
water saving technologies without risking increased sheath blight
incidence. We suggest that further cross-cutting research in this area
is warranted.

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates
Affect Rice Insect Populations and Diseases?} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
\\
A.H. Sparks\textsuperscript{\getAff{University of Southern Queensland}}\textsuperscript{*},
N.P. Castilla\textsuperscript{\getAff{International Rice Research Institute}},
B.A.R. Hadi\textsuperscript{\getAff{International Rice Research Institute}},
B.O. Sander\textsuperscript{\getAff{International Rice Research Institute}}\\
\bigskip
\textbf{\getAff{University of Southern Queensland}}Centre for Crop Health, West Street, Toowoomba, Queensland, Australia,
4350\\
\textbf{\getAff{International Rice Research Institute}}Los Baños, Laguna, Philippines, 4031\\
\bigskip
* Corresponding author: adam.sparks@usq.edu.au\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Water and nitrogen management play vital roles in rice production.
However, the mismanagement of these two management practices may trigger
sheath blight of rice, caused by \emph{Rhizoctonia solani}, which is
favored by wet conditions, high relative humidity, and high nitrogen
fertilizer levels. To understand how different combinations of water and
nitrogen management affect sheath blight epidemics, we conducted two
separate split-plot experiments with a water saving (alternate wetting
and drying) regime and traditional flood irrigation regime combined with
differing nitrogen treatments in the dry seasons of 2015 and 2016.
Disease was scored in the same way in both experiments using a sheath
blight assessment scale for field evaluation developed at the
International Rice Research Institute to assess the severity on infected
sheaths and leaves while sheath blight incidence on tillers were counted
per hill. We were unable to detect any differences in disease in either
experiment due to irrigation regime, N rates or the interaction of the
two treatments in either season. This suggests that farmers can adopt
water saving technologies without risking increased sheath blight
incidence. We suggest that further cross-cutting research in this area
is warranted.
